---
title: "Fall_2022_Panc_O_Glyco_Workflow_Preparation"
output: html_document
date: "2022-09-29"
---

Load In the Following Packages that will be Used Throughout the Script.  If you do not already have them installed will need to do so.
```{r}
# Load in Libraries
#load in the libraries
library(plyr)
library(tidyverse)
library(seqinr)
library(alakazam) 
#   if (!require("BiocManager", quietly = TRUE))
#     install.packages("BiocManager")
# 
# BiocManager::install("Biostrings")

# if (!require("BiocManager", quietly = TRUE))
#     install.packages("BiocManager")
# 
# BiocManager::install("GenomicAlignments")

library(tidytext)
library(ggplot2)
theme_set(theme_classic())
library(tidyr)
library(dplyr)
library(arsenal)
library(UpSetR)
library(ggupset)
library(viridis)
library(reshape2)
library(plotly)
library(readxl)
mytheme <- theme(legend.position = "none",
          plot.title = element_text(hjust = 0.5, face = "bold"),
          axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,))
``` 

# Import the Metamorpheus Data Files for the OGlyco PSM

Have 2877 rows and 44 Columns 
```{r}
DF1<-read.csv(("/Users/meganford/Documents/Research/9_2022_LC_Data_Panc_OGlyco_Workflow/oglycopsm.csv"))
```

# Filtering the Data from the GlycoDataset 
1) Zero Removed
2) 1929 rows remain
3) 1184 rows remain
4) 618 rows remain
5) 247 rows remain
```{r}
#1 Remove Decoys 
DF1 %>% filter(!grepl('DECOY',`Protein.Accession`))
#2 Remove Isoforms 
DF2<- DF1%>% filter(!grepl('\\|',`Protein.Accession`))
#3 Filter so only Level1 or Level1b
DF2<- DF2 %>% filter(grepl('Level1|Level1b',`GlycanLocalizationLevel`)) 
#4 Filter so only observe P12763 for BioFetuin
DF2<- DF2 %>% filter(grepl('P12763',`Protein.Accession`))
DF2<- DF2 %>% filter(QValue<0.01)


#5 extract the file name and create a column called Method
DF2$`File.Name` <-DF2$`File.Name` %>% 
  str_replace(".*09232022_", "")  # this gets rid of the first section of the file name 

DF2$method <-sub(".raw", "",DF2$`File.Name`) #this removes the end .raw portion of file name 
method_shortened <- str_split(DF2$method, "_", simplify = TRUE)
DF2$base_method <- method_shortened[,1] 

write.csv(DF2,"/Users/meganford/Documents/Research/9_2022_LC_Data_Panc_OGlyco_Workflow/filtered_oglycopsm.csv")


 DF2 %>% 
   group_by(`base_method`) %>%
   summarise("unique glycopeptides" = length(unique(Full.Sequence)))

  DF2 %>% 
   group_by(`base_method`) %>%
   summarise("unique glycopeptides" = length(Full.Sequence))
 
DF2 %>% 
   filter(`base_method` == "PNGasePosZTPos") %>% 
   summarise("unique glycopeptides" = unique(Plausible.GlycanComposition))

DF1 %>% 
   summarise("unique glycopeptides" = unique(Plausible.GlycanComposition))

```

The following Data analysis will use filtered_DF4:
  #Calculating Hydrophobicity and Average Sequence Length 

```{r}
###########Finding the hydrophobicity of the data##################
# Load required packages

# Use the Kidera et al, 1985 scores from the seqinr package

data(aaindex)
x <- aaindex[["KIDA850101"]]$I
# Rename the score vector to use single-letter codes
names(x) <- translateStrings(names(x), ABBREV_AA)
# Calculate hydrophobicity

filtered_DF4 <- DF2
filtered_DF4 <- filtered_DF4 %>% 
  mutate(gravy_score_knd = gravy(filtered_DF4$`Base.Sequence`),
         gravy_score_Kideria = gravy(filtered_DF4$`Base.Sequence`, hydropathy = x))

############Finding the length of the Base Sequence in eaach Row###########
filtered_DF4$Sequence_Length<-nchar(filtered_DF4$`Base.Sequence`)
filtered_DF4 <- filtered_DF4%>% relocate(Sequence_Length, .before = `Base.Sequence`)

############ Analysis of the Values for Hydrophobicity and Sequence Length
#I LIKE THIS WAY BETTER FOR SUMMARIZING ONE COLUMN AT A TIME
Summary_Sequence_Length <-filtered_DF4 %>% 
  group_by(`method`) %>%
  summarise(number_rows = n(),
            Mean_Sequence_Length = mean(Sequence_Length),
            Max_Sequence_Length = max(Sequence_Length),
            Min_Sequence_Length = min(Sequence_Length),
            SD_Sequence_Length = sd(Sequence_Length),
            Range_Sequence_Length = range(Sequence_Length))
Summary_Sequence_Length <-distinct(Summary_Sequence_Length, method, .keep_all = TRUE) 
Summary_Sequence_Length

Summary_Sequence_Length_base <-filtered_DF4 %>% 
  group_by(`base_method`) %>%
  summarise(number_rows = n(),
            Mean_Sequence_Length = mean(Sequence_Length),
            Max_Sequence_Length = max(Sequence_Length),
            Min_Sequence_Length = min(Sequence_Length),
            SD_Sequence_Length = sd(Sequence_Length),
            Range_Sequence_Length = range(Sequence_Length))
Summary_Sequence_Length_base <-distinct(Summary_Sequence_Length_base, base_method, .keep_all = TRUE) 
Summary_Sequence_Length_base

Summary_gravy_score_knd <-filtered_DF4 %>% 
  group_by(`method`) %>%
  summarise(number_rows = n(),
            Mean_gravy_score_knd = mean(gravy_score_knd),
            Max_gravy_score_knd = max(gravy_score_knd),
            Min_gravy_score_knd = min(gravy_score_knd),
            SD_gravy_score_knd = sd(gravy_score_knd),
            Range_gravy_score_knd = range(gravy_score_knd))
Summary_gravy_score_knd <-distinct(Summary_gravy_score_knd, method, .keep_all = TRUE) 
Summary_gravy_score_knd

Summary_gravy_score_knd_base <-filtered_DF4 %>% 
  group_by(`base_method`) %>%
  summarise(number_rows = n(),
            Mean_gravy_score_knd = mean(gravy_score_knd),
            Max_gravy_score_knd = max(gravy_score_knd),
            Min_gravy_score_knd = min(gravy_score_knd),
            SD_gravy_score_knd = sd(gravy_score_knd),
            Range_gravy_score_knd = range(gravy_score_knd))
Summary_gravy_score_knd_base <-distinct(Summary_gravy_score_knd_base, base_method, .keep_all = TRUE) 
Summary_gravy_score_knd_base
```



```{r}
#DENSITY PLOTS OF THE Hydrophobicity vs BASE METHOD 
ggplot(filtered_DF4, aes(x = gravy_score_knd, fill=base_method)) + 
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "white") +
  geom_density(alpha=.6)+
  facet_wrap(~base_method)+
  labs(title = "Hydrophobicity Score",
       x = "Hydrophobicity Score (KnD)",
       y = "Density") +
  scale_fill_manual(values=c("#e27c7c", "#6d4b4b", "#333333", "#466964","#599e94", "#6cd4c5")) + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

#DENSITY PLOTS OF THE Base Sequence Length for BASE METHOD 
ggplot(filtered_DF4, aes(x = Sequence_Length, fill=base_method)) + 
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "white") +
  geom_density(alpha=.6)+
  facet_wrap(~base_method)+
  labs(title = "Sequence Length",
       x = "Sequence Length",
       y = "Density") +
  scale_fill_manual(values=c("#e27c7c", "#6d4b4b", "#333333", "#466964","#599e94", "#6cd4c5")) + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
```


```{r}
filtered_DF4 %>% 
  ggplot( aes(x=base_method, y=gravy_score_knd, fill=base_method, alpha=base_method)) +
  geom_boxplot(alpha = 0.6) +
  scale_fill_manual(values=c("#e27c7c", "#6d4b4b", "#333333", "#466964","#599e94", "#6cd4c5")) +
  labs(title ="Boxplot of Gravy Scores for each Sample Preparation Method", 
       x="Enrichment Method", 
       y = "Gravy Score (knd)", 
       color ="black") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = "none")

filtered_DF4 %>% 
  ggplot(aes(y = gravy_score_knd, x = method, fill = base_method)) +
  geom_boxplot(alpha = 0.6) +
  scale_fill_manual(values=c("#e27c7c", "#6d4b4b", "#333333", "#466964","#599e94", "#6cd4c5"))+
  labs(title ="Boxplot of Gravy Scores for each Sample Preparation Method", 
       x="Enrichment Method", 
       y = "Gravy Score (knd)", 
       color ="black") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


filtered_DF4 %>% 
  ggplot(aes(x=base_method, y=gravy_score_knd, fill=base_method, alpha=base_method)) +
  geom_violin(aes(fill=base_method), trim=FALSE, position = position_dodge(0.9),alpha =0.6, show.legend = FALSE) +
  theme_classic() +
  geom_boxplot(width = 0.15, position = position_dodge(0.9), show.legend = FALSE)  +
  theme(legend.position = "none") +
  scale_fill_manual(values=c("#e27c7c", "#6d4b4b", "#333333", "#466964","#599e94", "#6cd4c5")) +
  labs(title ="Violin Plot of Gravy Scores for each Sample Preparation Method", 
       x="Enrichment Method", 
       y = "Gravy Score (knd)", 
       color ="black") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = "none")

filtered_DF4 %>% 
  ggplot(aes(y = gravy_score_knd, x = base_method, fill = base_method)) +
  geom_violin(aes(fill=base_method), trim=FALSE, position = position_dodge(0.9),alpha =0.6, show.legend = FALSE) +
  theme_classic() +
  geom_boxplot(width = 0.15, position = position_dodge(0.9), show.legend = FALSE)  +
  theme(legend.position = "none") +
  scale_fill_manual(values=c("#e27c7c", "#6d4b4b", "#333333", "#466964","#599e94", "#6cd4c5")) +
  labs(title ="Violin Plot of Gravy Scores for each Sample Preparation Method", 
       x="Enrichment Method", 
       y = "Gravy Score (knd)", 
       color ="black") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```



# Greating Gravy Plots
### Creating Gravy Plots for all the data individual Methods not seperated
```{r}

#Sorting the the KnD gravy scores from low to high
filtered_DF4 <- filtered_DF4 %>% 
  arrange(gravy_score_knd)

filtered_DF4_hydrophobicity <- filtered_DF4 %>%
  distinct(gravy_score_knd,method,base_method)  %>% 
  mutate(id = row_number())

filtered_DF4_hydrophobicity %>% 
  ggplot(aes(x=id, y=gravy_score_knd, fill=base_method, color=base_method)) + geom_bar(stat="identity", show.legend = FALSE)  +
  theme_classic() +
  theme(plot.title=element_text(face="bold"))  +     theme_classic() +
  theme(legend.position = "none")  +
  labs(title ="Gravy Plot for All Sample Preparation Method", 
       x="Rank", 
       y = "Gravy Score (knd)", 
       color ="black") + mytheme


filtered_DF4_hydrophobicity %>% 
  ggplot(aes(x=id, y=gravy_score_knd,  fill=method,color=method)) + 
  geom_bar(stat="identity", show.legend = FALSE ) + 
  facet_wrap(~method) +
  scale_fill_manual(values=c("#0000b3", "#0010d9", "#0020ff", "#0040ff", "#0060ff", "#0080ff", "#009fff", "#00bfff", "#00ffff","#54bebe", "#76c8c8", "#98d1d1", "#badbdb", "#dedad2", "#e4bcad", "#df979e", "#d7658b", "#c80064","#e27c7c", "#a86464", "#6d4b4b", "#503f3f", "#333333", "#3c4e4b", "#466964", "#599e94", "#6cd4c5","#333333", "#3c4e4b", "#466964", "#599e94", "#6cd4c5")) +
  scale_color_manual(values=c("#0000b3", "#0010d9", "#0020ff", "#0040ff", "#0060ff", "#0080ff", "#009fff", "#00bfff", "#00ffff","#54bebe", "#76c8c8", "#98d1d1", "#badbdb", "#dedad2", "#e4bcad", "#df979e", "#d7658b", "#c80064","#e27c7c", "#a86464", "#6d4b4b", "#503f3f", "#333333", "#3c4e4b", "#466964", "#599e94", "#6cd4c5","#333333", "#3c4e4b", "#466964", "#599e94", "#6cd4c5")) +
  labs(title ="Gravy Plot for each Sample Preparation Method", 
       x="Enrichment Method", 
       y = "Gravy Score (knd)", 
       color ="black") + mytheme

filtered_DF4_hydrophobicity %>% 
  ggplot(aes(x=id, y=gravy_score_knd,  fill=method,color=method)) + geom_bar(stat="identity", show.legend = FALSE ) + 
  facet_wrap(~method) +
  scale_fill_hue() +
  scale_color_hue() +
  theme_classic() +
  theme(legend.position = "none")  +
  labs(title ="Gravy Plot for each Sample Preparation Method", 
       x="Enrichment Method", 
       y = "Gravy Score (knd)", 
       color ="black") + 
  mytheme

filtered_DF4_hydrophobicity %>% 
  ggplot(aes(x=id, y=gravy_score_knd,  fill=method,color=method)) + geom_bar(stat="identity", show.legend = FALSE ) + 
  facet_wrap(~method) +
  scale_fill_viridis_d() +
  scale_color_viridis_d() +
  theme_classic() +
  theme(legend.position = "none")  +
  labs(title ="Gravy Plot for each Sample Preparation Method", 
       x="Enrichment Method", 
       y = "Gravy Score (knd)", 
       color ="black") + mytheme

filtered_DF4_hydrophobicity %>% 
  ggplot(aes(x=id, y=gravy_score_knd,  fill=base_method)) + geom_bar(stat="identity") + 
  scale_fill_manual(values=c("#e27c7c", "#6d4b4b", "#333333", "#466964","#599e94", "#6cd4c5"))  +
  labs(title ="Gravy Plot with All Sample Preparation Methods Ranked Together", 
       x="Rank", 
       y = "Gravy Score (knd)", 
       color ="black") + mytheme +
  theme(plot.title=element_text(size=10))

```




# Creating Gravy Plots for all the data individual Methods seperated
### Plots ranking within each method and Run
```{r}
#Filtering out distinct values by the method

#Arranging from LOW to High within each method then ranking
filtered_DF4_hydrophobicity_method <- filtered_DF4 %>%
  arrange(gravy_score_knd) %>% 
  group_by(method) %>% 
  distinct(gravy_score_knd,method,base_method)
filtered_DF4_hydrophobicity_method <- filtered_DF4_hydrophobicity_method %>%
  group_by(method) %>% 
  mutate(id = row_number())
filtered_DF4_hydrophobicity_method

filtered_DF4_hydrophobicity_method %>% 
  ggplot(aes(x=id, y=gravy_score_knd, color = method)) + 
  geom_bar(stat="identity",show.legend = FALSE ) + 
  facet_wrap(~method) + 
  labs(title = "Hydrophobicity Score",
       x = "ID number",
       y = "Hydrophobicity Score (KnD)") + mytheme +
  theme(strip.text.x = element_text(size = 6))
```
### Plots ranking Gravy Scores within each method
```{r}
#Filtering out distinct values by the method
#Arranging from LOW to High within each method then ranking
filtered_DF4_hydrophobicity_basemethod <- filtered_DF4 %>%
  arrange(gravy_score_knd) %>% 
  group_by(base_method) %>% 
  distinct(gravy_score_knd,method,base_method)
filtered_DF4_hydrophobicity_basemethod <- filtered_DF4_hydrophobicity_method %>%
  group_by(base_method) %>% 
  mutate(id = row_number())
filtered_DF4_hydrophobicity_basemethod

#FACET PLOT
filtered_DF4_hydrophobicity_basemethod %>% 
  ggplot(aes(x=id, y=gravy_score_knd, color = base_method)) + 
  geom_bar(stat="identity",show.legend = FALSE, alpha = 0.6 ) + 
  facet_wrap(~base_method) + 
  scale_color_manual(values=c("#e27c7c", "#6d4b4b", "#333333", "#466964","#599e94", "#6cd4c5")) +
  labs(title = "Hydrophobicity Score vs. Rank",
       x = "ID number",
       y = "Hydrophobicity Score (KnD)") + mytheme +
  theme(strip.text.x = element_text(size = 6))


#scale_color_manual(values=c("#e27c7c", "#6d4b4b", "#333333", "#466964","#599e94", "#6cd4c5"))

#RAX GRAVY PLOT                
filtered_DF4_hydrophobicity_basemethod %>% 
  filter(base_method=="PNGasePosZTPos") %>% 
  ggplot(aes(x=id, y=gravy_score_knd, fill = base_method)) + 
  scale_fill_manual(values = c("#6cd4c5")) + 
  geom_bar(stat="identity",show.legend = FALSE) + 
  labs(title = "Hydrophobicity Score vs. Rank - PNGasePosZTPos",
       x = "ID number",
       y = "Hydrophobicity Score (KnD)") + mytheme +
  theme(strip.text.x = element_text(size = 6))

#"#e27c7c", "#6d4b4b", "#333333", "#466964","#599e94", "#6cd4c5"

#ERLIC GRAVY PLOT                
filtered_DF4_hydrophobicity_basemethod %>% 
  filter(base_method=="PNGaseNegZTPos") %>% 
  ggplot(aes(x=id, y=gravy_score_knd, fill = base_method)) + 
  geom_bar(stat="identity",show.legend = FALSE) +
  scale_fill_manual(values = c("#6d4b4b")) +
  labs(title = "Hydrophobicity Score vs. Rank - PNGaseNegZTPos",
       x = "ID number",
       y = "Hydrophobicity Score (KnD)") + mytheme +
  theme(strip.text.x = element_text(size = 6))

#OGlycoControl GRAVY PLOT                
filtered_DF4_hydrophobicity_basemethod %>% 
  filter(base_method=="PNGasePosZTNeg") %>% 
  ggplot(aes(x=id, y=gravy_score_knd, fill = base_method)) + 
  scale_fill_manual(values = c("#599e94")) + 
  geom_bar(stat="identity",show.legend = FALSE) + 
  labs(title = "Hydrophobicity Score vs. Rank - PNGasePosZTNeg",
       x = "ID number",
       y = "Hydrophobicity Score (KnD)") + mytheme +
  theme(strip.text.x = element_text(size = 6))

#BAHpH GRAVY PLOT                
filtered_DF4_hydrophobicity_basemethod %>% 
  filter(base_method=="PNGaseNegZTNeg") %>% 
  ggplot(aes(x=id, y=gravy_score_knd, fill = base_method)) + 
  scale_fill_manual(values = c("#e27c7c")) + 
  geom_bar(stat="identity",show.legend = FALSE ) + 
  labs(title = "Hydrophobicity Score vs. Rank - PNGaseNegZTNeg",
       x = "ID number",
       y = "Hydrophobicity Score (KnD)") + mytheme +
  theme(strip.text.x = element_text(size = 6))

```
# Comparing Glycans Compositions Identified in each experiment type using Heatmaps - Keeping all of the rows (no filtering to unique)
```{r}
#Start by creating a dataframe that groups together by the base method and the glycan composition.  We add a column for count that indicates how many times we see the plausible glycan composition within each method
filtered_DF4_count <- filtered_DF4 %>%   # Applying group_by & summarise
  group_by(base_method, `Plausible.GlycanComposition`) %>%
  summarise(count = n())
filtered_DF4_count

#To plot the data into a heatmap we need to pivot the table.  This means instead of one column with all plausible glycan compositions we get a column for each composition.
pivot_filtered_DF4_count <- pivot_wider(filtered_DF4_count, names_from = `Plausible.GlycanComposition`, values_from = count)
pivot_filtered_DF4_count[is.na(pivot_filtered_DF4_count)] = 0
pivot_filtered_DF4_count

#For the heatmaply package we Take the First row which has the base_method and make it into a rowname
heatmap<-pivot_filtered_DF4_count %>% remove_rownames %>% column_to_rownames(var="base_method")

#WE now create our interactive heat map with the heatmaply package
#DOCUMENTATION: https://www.datanovia.com/en/blog/how-to-create-a-beautiful-interactive-heatmap-in-r/
#I choose to use heatmaply because it will normalize our data for us

library(heatmaply)
heatmaply(normalize(heatmap),
          plot_method = "plotly",
          main = "Heatmap of the Glycan Compositions Observed in Each Method",
          xlab = "Plausible Glycans",
          ylab = "Method",colors = viridis(n = 256,  option = "magma"),
          column_text_angle = 90)

heatmaply(heatmap,
          plot_method = "plotly",
          main = "Heatmap of the Glycan Compositions Observed in Each Method",
          xlab = "Plauisble Glycans",
          ylab = "Method",colors = viridis(n = 256,  option = "magma"),
          column_text_angle = 90)


#THESE ARE THE SAME PLOTS IN ANOTHER COLOR SCHEME
heatmaply(normalize(heatmap),
          plot_method = "plotly",
          main = "Normalized Heatmap of the Glycan Compositions Observed in Each Method",
          xlab = "Plausible Glycans",
          ylab = "Method",
          column_text_angle = 90)

heatmaply(heatmap, 
          plot_method = "plotly",
          main = "Heatmap of the Glycan Compositions Observed in Each Method",
          xlab = "Plausible Glycans",
          ylab = "Method",
          column_text_angle = 90)
```

############## NEW CODE HERE 

To see how many plausible Glycan Compositions we start with, how many are unique,etc. : 
length(filtered_DF4$Plausible.GlycanComposition)
[1] 618 

length(unique(filtered_DF4$Plausible.GlycanComposition))
[1] 10

unique(filtered_DF4$Plausible.GlycanComposition)
 [1] "H1N1A1" "H1N1"   "N1"     "H2N2A2" "H2N2A1" "H1N1A2" "H2N2"   "H1N2A1" "N1A1"   "H1N2"
 
#UPSET PLOT for Plausible Glycan Structure
```{r}
### EACH BASE METHOD FILTERED
PNGasePosZTPos <- filtered_DF4 %>% 
  filter(base_method=="PNGasePosZTPos")
PNGaseNegZTPos <- filtered_DF4 %>% 
  filter(base_method=="PNGaseNegZTPos")
PNGasePosZTNeg<- filtered_DF4 %>% 
  filter(base_method=="PNGasePosZTNeg")
PNGaseNegZTNeg<- filtered_DF4 %>% 
  filter(base_method=="PNGaseNegZTNeg")

x_upset = list(PNGasePosZTPos = PNGasePosZTPos$`Plausible.GlycanComposition`,
               PNGaseNegZTPos = PNGaseNegZTPos$`Plausible.GlycanComposition`,
               PNGasePosZTNeg = PNGasePosZTNeg$`Plausible.GlycanComposition`,
               PNGaseNegZTNeg = PNGaseNegZTNeg$`Plausible.GlycanComposition`)
library(UpSetR)
upset(fromList(x_upset), order.by = "freq",matrix.color = "black", main.bar.color = "black",,mainbar.y.label = "Sample Preparation Method Intersections", sets.x.label = "Glycans Per Method" )
```

#Investigating Glycans from the oGlycoPSM filtered file: 
Starting Here with the Excel File I modified from the filtered_DF4 to extract the glycans manually
The metamorpheus program currently support the following
monosaccharides. {"Hex"},{"HexNAc"},{"NeuAc"},{"NeuGc"},{"Fuc"},{"Phospho"},{"Sulfo"},{"Na"},{"Ac"},{"Xylose" }

Excel showed only H,A,N, and F


Writting out code: 

for x = H, N, A, and F 
if column plausible glycan composition contains X 
then take # after X and place into new column labeled glycan_H
else continue

Examples 
x <- -5
if(x > 0){
print("Non-negative number")
} else {
print("Negative number")
}

str = "H1N1" 
chars = "H"

#want to identify if the string in row contains character of interest ()
if (grepl(chars, str, fixed = TRUE)) {
print("We found the character")

} else {
print("We did not find the character")
}

 df <- data.frame(V1 = c("H1N1, H2N2", "H2F3"),
      spl <-strsplit(as.character(df$V1), ",")
data.frame(V1= sapply(spl, "[", 1))

```{r}
DF_glycans <-filtered_DF4

DF_glycans[is.na(DF_glycans)] = 0

DF_unique_glycans <-DF_glycans %>%
  group_by(method) %>%
  summarise(n = n_distinct(`Plausible.GlycanComposition`))
DF_unique_glycans

DF_mean<-aggregate(cbind(glycan_A,glycan_F,glycan_H,glycan_N) ~ `base_method`, DF_glycans, mean)

DF_sum<-aggregate(cbind(glycan_A, glycan_F,glycan_H,glycan_N) ~ `base_method`, DF_glycans, sum)
DF_mean
DF_sum

DF_mean_pivot<- DF_mean %>%
  pivot_longer(glycan_A:glycan_N, names_to = "Glycan_type", values_to = "Count_Glycans")

DF_sum_pivot<- DF_sum %>%
  pivot_longer(glycan_A:glycan_N, names_to = "Glycan_type", values_to = "Count_Glycans")

DF_glycans_pivot<- DF_glycans%>%
  pivot_longer(glycan_H:glycan_F, names_to = "Glycan_type", values_to = "Count_Glycans")

unique(DF_glycans$`Plausible GlycanComposition`)

#PLOT 1: 
ggplot(data=DF_sum_pivot, aes(x=Glycan_type, y=Count_Glycans, fill=base_method)) + geom_bar(stat="identity") + theme_bw() +
  labs(title = "Glycan Counts",
       x = "Glycan Type",
       y = "Glycan Count") +
  theme(plot.title=element_text(face="bold"))

#PLOT 3:
ggplot(DF_sum_pivot, aes(x=base_method, y=Glycan_type, fill=Count_Glycans)) + 
  geom_tile() + 
  theme_minimal() +
  scale_fill_viridis_b() +
  theme(axis.text.x=element_text(           # Vertical text on x axis
    angle=90,vjust=0.5,hjust=1))   

#PLOT 4: 
ggplot(data=DF_mean_pivot, aes(x=Glycan_type, y=Count_Glycans, fill=base_method)) + geom_bar(stat="identity") + theme_bw() +
  labs(title = "Glycan Counts",
       x = "Glycan Type",
       y = "Glycan Count") +
  theme(plot.title=element_text(face="bold"))

#PLOT 5:
ggplot(data=DF_mean_pivot, aes(x=Glycan_type, y=Count_Glycans, fill=base_method)) + geom_bar(stat="identity") + theme_bw() +
  facet_wrap(~base_method) +
  labs(title = "Glycan Counts",
       x = "Glycan Type",
       y = "Glycan Count") +
  theme(plot.title=element_text(face="bold"))

#PLOT 6:
ggplot(DF_mean_pivot, aes(x=base_method, y=Glycan_type, fill=Count_Glycans)) + 
  geom_tile() + 
  theme_minimal() +
  scale_fill_viridis_b() +
  theme(axis.text.x=element_text(           # Vertical text on x axis
    angle=90,vjust=0.5,hjust=1))
#Plot 7 
ggplot(DF_glycans_pivot, aes(x=Glycan_type, y=`Protein.Accession`, fill=Count_Glycans)) + 
  geom_tile() + 
  facet_wrap(~base_method) +
  theme_minimal() +
  scale_fill_viridis_b() +
  theme(axis.text.x=element_text(           # Vertical text on x axis
    angle=90,vjust=0.5,hjust=1))

# glycan_matrix<-with(DF_glycans_pivot, table(`Protein Accession`,`Glycan_type`))
# 
# my_colors <- colorRampPalette(c("cyan", "deeppink3")) 
# heatmap(glycan_matrix, col=my_colors(100))
# heatmap(glycan_matrix)

DF_mean_pivot %>% 
  ggplot( aes(x=Glycan_type, y=Count_Glycans, fill=base_method, alpha=base_method)) +
  geom_boxplot(alpha = 0.6) +
  scale_fill_manual(values=c("#e27c7c", "#6d4b4b", "#333333", "#466964","#599e94", "#6cd4c5")) +
  labs(title ="Boxplot of Gravy Scores for each Sample Preparation Method", 
       x="Enrichment Method", 
       y = "Count_Glycans", 
       color ="black") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) #+
#theme(legend.position = "none")

#PLOT 2:
ggplot(data=DF_sum_pivot, aes(x=Glycan_type, y=Count_Glycans, fill=base_method)) + geom_bar(stat="identity") + theme_bw() +
  facet_wrap(~base_method) +
  labs(title = "Glycan Counts",
       x = "Glycan Type",
       y = "Glycan Count") +
  theme(plot.title=element_text(face="bold"))

#PLOT 2:
ggplot(data=DF_mean_pivot, aes(x=Glycan_type, y=Count_Glycans, fill=base_method)) + geom_bar(stat="identity") +
  facet_wrap(~base_method) +
  labs(title = "Mean Glycan Counts per Method",
       x = "Glycan Type",
       y = "Mean Glycan Count") + mytheme  +
  scale_fill_manual(values=c("#e27c7c", "#6d4b4b", "#333333", "#466964","#599e94", "#6cd4c5")) +
  theme(plot.title=element_text(face="bold")) 
```
Boxplot and Violin Plot of Monosaccharides per Glycan for each sample Preparation Method
```{r}
DF_glycans_pivot %>% 
  ggplot(aes(x=Glycan_type, y=Count_Glycans, fill=base_method, alpha=base_method)) +
  geom_boxplot(aes(fill=base_method),alpha =0.6, show.legend = FALSE) + facet_wrap(~base_method) + 
  theme_classic() +
  theme(legend.position = "none") +
  scale_fill_manual(values=c("#e27c7c", "#6d4b4b", "#333333", "#466964","#599e94", "#6cd4c5")) +
  labs(title ="Monosaccharides per Glycan for each Sample Preparation Method", 
       x="Monosaccharides", 
       y = "Number of Glycans", 
       color ="black") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = "none") + mytheme +
  theme(plot.title=element_text(size=10))

DF_glycans_pivot %>% 
  ggplot(aes(x=Glycan_type, y=Count_Glycans, fill=base_method, alpha=base_method)) +
  geom_violin(aes(fill=base_method), trim=FALSE, position = position_dodge(0.9),alpha =0.6, show.legend = FALSE) + facet_wrap(~base_method) + 
  theme_classic() +
  geom_boxplot(width = 0.2, position = position_dodge(0.9), show.legend = FALSE)  +
  theme(legend.position = "none") +
  scale_fill_manual(values=c("#e27c7c", "#6d4b4b", "#333333", "#466964","#599e94", "#6cd4c5")) +
  labs(title ="Violin Plot of Monosaccharides per Glycan for each Sample Preparation Method", 
       x="Monosaccharides", 
       y = "Nubmer of Glycans", 
       color ="black") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = "none") + mytheme +
  theme(plot.title=element_text(size=10))
```


